\documentclass[20pt]{article}

\usepackage[a4paper, margin=2cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{times}
\usepackage{tipa}
\usepackage{covington}
\usepackage{tikz-qtree}

\setlength\parindent{0pt}
\newcommand{\ipa}[1]{\textipa{#1}}
\newcommand{\broad}[1]{/\ipa{#1}/}
\newcommand{\narrow}[1]{[ \ipa{#1} ]}
\newcommand{\english}[1]{$<$#1$>$}
\newcommand{\sk}[0]{{\kern 0.05em}}
\newcommand{\mk}[0]{{\kern 0.1em}}
\newcommand{\smallcapi}[0]{\sk\textsci\sk}
\newcommand{\openo}[0]{\sk O}

\begin{document}

\Large\textbf{Problem Set 1: Mad Libs} \\
\normalsize
Alice McKean \\
\today

One problem with the mad libs theory is that it does not allow for word-phrase
substitution. Take for instance the sentence generator ``$<$noun$>$ went
swimming.''. A valid instantiation of this generator looks like ``Janice went
swimming.''.  This generator doesn't capture the real structure of sentences like
``$<$x$>$ went swimming.''. For instance the sentence ``Janice and Tom went
swimming.'' is syntactically valid but not permissible under the generator. This
problem isn't unique to nouns but occurs in every major lexical category.
``Hariet went $<$verb$>$ after work'' is a sentence generator that does not
allow for
``Hariet went swimming and running after
work.''.
``We saw the movie $<$preposition$>$ midnight'' is a sentence generator that
does not allow for ``We saw the movie before and after midnight''.
\\

The mad libs theory doesn't enforce agreement between words either. Take for
instance the sentence generator ``The $<$noun$>$ is awake.''.  ``The dog is awake.'' is
syntactically valid but ``The children is awake.'' is not. In this example the mad
libs theory is not accounting for number agreement between the noun and verb. \\

Consider a sentence generator full of adjectives like ``I saw a $<$adj$>$
$<$adj$>$ $<$adj$>$ $<$adj$>$ car''. A sensible instantiation of this generator
is ``I saw a really small old red car''. If you flip the adjective order around 
the sentence becomes ``I saw a red old small really car'' which sounds terrible.
This shows that the mad lib theory doesn't account for english adjective order.



\end{document}

